\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}	
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}	
\usepackage{url}


%%% Custom sectioning
\usepackage{sectsty}
\allsectionsfont{\centering \normalfont\scshape}


%%% Custom headers/footers (fancyhdr package)
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead{}											% No page header
\fancyfoot[L]{}											% Empty 
\fancyfoot[C]{}											% Empty
\fancyfoot[R]{\thepage}									% Pagenumbering
\renewcommand{\headrulewidth}{0pt}			% Remove header underlines
\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
\setlength{\headheight}{13.6pt}


%%% Equation and float numbering
\numberwithin{equation}{section}		% Equationnumbering: section.eq#
\numberwithin{figure}{section}			% Figurenumbering: section.fig#
\numberwithin{table}{section}				% Tablenumbering: section.tab#


%%% Maketitle metadata
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule

\title{
		%\vspace{-1in} 	
		\usefont{OT1}{bch}{b}{n}
		\normalfont \normalsize \textsc{University of Science and Technology of Hanoi \\ Master ICT} \\ [25pt]
		\horrule{0.5pt} \\[0.4cm]
		\huge Practical 1 \\
		\horrule{2pt} \\[0.5cm]
}
\author{
		\normalfont 								\normalsize
        St. Tran Quy Ban\\[-3pt]		\normalsize
        \today
}
\date{}


%%% Begin document
\begin{document}
\maketitle

\section{BASH, PIPE and I/O Redirection}

\begin{itemize}
	\item 1. List everyone logged in and save the list in a file called "users" in your own home directory.
	
	Answer: Using the w command to find users who logged into the system. We can use "who -u" to list users logged in.
	\item 2. List all processes that are running and add this list to the end of the "users" file.
	
	Answer: Using "ps A" command to list all processes that are running.
	
	\item 3. List everyone who is logged on sorted by their username.
	
	Answer: w | sort
	
	\item 4. Count number of session each logged in user, sorted by this number in descending order.
	
	Answer: w | sort -r
	\item 5. Show content of the first and last 3 lines of the file "/etc/fstab"
	
	Answer:  
	head -3 /etc/fstab
	tail -3 /etc/fstab
	
	My Macbook OS does not have those files so I could not run the command sucessfully.
	
	The format to show content of any file is: head [or] tail - [n] "file name".
	
	\item 6. Retrieve line number 5 to 10 from the file "/etc/fstab" and write these files into a new file "extract.txt"
	
	Answer: 
	In order to retrieve the content of a file, we can use several Linux commands such as "cat", "more", "less", "awk", or sed ("cat" is usually used for concatenate files).
	In these situation I prefer the command "sed". The format of this command as follows: sed -n '1, \$p' file.
	
	sed -n '5, 10p' /etc/fstab
	
	to write these files into a new file "extract.txt" I use the command: 
	
	
	\item 7. List all files in current directory, recursively, to which the user has full permission.
	
	Answer: The command ls will help to list all files in the curent directory. 
	ls -rf
	
	\item 8. Compare two files and show percentage of similarities between them.
	
	Answer: 
	
	diffLines=`diff \$1 \$2 | egrep "\^(>|<)" | wc -l`
	
	aLines=`wc -l < \$1`
	
	bLines=`wc -l < \$2`
	
	if [ \$ aLines -eq 0 ] \&\& [ \$ bLines -eq 0 ]; then
	
		exit 0
		
	fi
	
	diffPer=`echo "\$ diffLines * 100 * 2 / (\$ aLines + \$ bLines)" | bc`
	
	similar=`echo "100-\$ diffPer" | bc`
	
	if [ "\$ similar" -gt 90 ]; then
	
		echo Similarity \$ similar: \$1 \$2
		
	fi	
	
	\item 9. Find all files in current directory, recursively, that are at least 90 percent similar
	
	Answer:  
	
    
   
\end{itemize}

\section{Appendix}

\begin{itemize}
	\item Question 1.
	
	16:32  up  5:43, 2 users, load averages: 2.01 1.66 1.68
	USER     TTY      FROM              LOGIN@  IDLE WHAT
	BillyTran console  -                11:06    5:25 -
	BillyTran s001     -                16:32       - w
	BillyTran@Trans-MacBook-Air sa2020 % who -u
	BillyTran console  Mar 11 09:36 02:08 	   178
	BillyTran ttys000  Mar 11 11:02   .   	  1519
	
	\item Question 2.
	1013   ??  Ss     0:02.32 /Applications/Dropbox.app/Contents/PlugIns/garcon.ap
	 1017   ??  S      0:00.27 /System/Library/Frameworks/CoreServices.framework/Fr
	 1018   ??  S      0:00.41 /System/Library/Frameworks/CoreServices.framework/Fr
	 1024   ??  S      0:00.56 /System/Library/Frameworks/CoreServices.framework/Fr
	 1025   ??  S      0:00.76 /System/Library/Frameworks/CoreServices.framework/Fr
	 1077   ??  S      0:00.18 /System/Library/Frameworks/CoreServices.framework/Fr
	 1078   ??  S      0:00.19 /System/Library/Frameworks/CoreServices.framework/Fr
	 1080   ??  S      0:00.18 /System/Library/Frameworks/CoreServices.framework/Fr
	 1083   ??  S      0:00.19 /System/Library/Frameworks/CoreServices.framework/Fr
	 1084   ??  S      0:00.09 /System/Library/Frameworks/CoreServices.framework/Fr
	 1088   ??  S      0:00.13 /System/Library/Frameworks/CoreServices.framework/Fr
	 1089   ??  S      0:00.13 /System/Library/Frameworks/CoreServices.framework/Fr
	 1090   ??  S      0:00.10 /System/Library/Frameworks/CoreServices.framework/Fr
	 1091   ??  S      0:00.10 /System/Library/Frameworks/CoreServices.framework/Fr
	 1093   ??  S      0:00.33 /System/Library/Frameworks/CoreServices.framework/Fr
	 1094   ??  S      0:00.78 /System/Library/Frameworks/CoreServices.framework/Fr
	 1095   ??  S      0:00.82 /System/Library/Frameworks/CoreServices.framework/Fr
	 1111   ??  S      0:05.23 /System/Applications/Utilities/Terminal.app/Contents
	 1117   ??  S      0:02.73 /Applications/Sublime Text.app/Contents/MacOS/Sublim
	 1118   ??  Ss     0:00.47 /Applications/Dropbox.app/Contents/PlugIns/garcon.ap
	 1119   ??  S      0:00.48 /Applications/Sublime Text.app/Contents/MacOS/plugin
	 1128   ??  Ss     0:00.05 /usr/sbin/ocspd
	 1129   ??  S      0:00.13 /System/Library/PrivateFrameworks/DistributedEvaluat
	 1112 s001  Ss     0:00.05 login -pf BillyTran
	 1113 s001  S      0:00.08 -zsh
	 1131 s001  R+     0:00.01 ps A
	
	\item Question 3.
	
	BillyTran@Trans-MacBook-Air sa2020 % w | sort 
	11:46  up  2:15, 2 users, load averages: 1.89 1.82 1.75
	BillyTran console  -                 9:36    2:09 -
	BillyTran s000     -                11:02       - sort
	USER     TTY      FROM              LOGIN@  IDLE WHAT
	
	\item Question 4.
	USER     TTY      FROM              LOGIN@  IDLE WHAT
	BillyTran s000     -                11:02       - sort -r
	BillyTran console  -                 9:36    6:51 -
	16:28  up  6:56, 2 users, load averages: 1.24 1.60 1.77
	
	\item Question 6.
	.
	..
	Practical1.pdf
	Practical1.tex
	Qestion 1: BillyTran@Trans-MacBook-Air ~ % w
	Practical1.synctex.gz
	README.md
	.git
	Practical1.aux
	Practical1.log
	
\end{itemize}

%%% End document
\end{document}